Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-18 vesicle_code/docs/adhesion/adhesion.tex
rearranged some figs

\begin{figure}[htp]
  \includegraphics[width=0.5\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \caption{\label{fig:extensionalPhaseDiagram} Phase diagram of vesicle
  hydrodynamics in an extensional flow.  At a fixed Hamaker constant
  $H=0.7$ and adhesion length scale $\delta=0.4$.  For small extensional
  rates, the doublet structure is not broken (blue marks), while at
  large extensional rates, the doublet is broken (red marks).}
\end{figure}

@@

\todo[inline]{Plot of the final inclination angle of doublets that
survive the extensional rate}

\begin{figure}[htp]
  \begin{minipage}{0.6\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $0.70$ submerged in an extensional flow with an extensional rate of
  $\chi$. {\em Right}: The definition of the inclination angle.  An
  inclination angle of $\pi$ indicates a doublet whose long axis is
  parallel to the converging direction, while an inclination angle of
  $\pi/2$ indicates a doublet whose short axis is parallel to the
  converging direction.}
\end{figure}

>>>>

\begin{figure}[htp]
  \begin{minipage}{0.6\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}:Phase diagram
  of vesicle hydrodynamics in an extensional flow.  At a fixed Hamaker
  constant $H=0.7$ and adhesion length scale $\delta=0.4$.  For small
  extensional rates, the doublet structure is not broken (blue marks),
  while at large extensional rates, the doublet is broken (red marks).
  {\em Right}: The definition of the inclination angle.  An inclination
  angle of $\pi$ indicates a doublet whose long axis is parallel to the
  converging direction, while an inclination angle of $\pi/2$ indicates
  a doublet whose short axis is parallel to the converging direction.}
\end{figure}

@@

\begin{figure}[htp]
  \begin{minipage}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\textwidth}
    \todo[inline]{Plot of the final inclination angle of doublets that
    survive the extensional rate}
  \end{minipage}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $0.70$ submerged in an extensional flow with an extensional rate of
  $\chi$.}
\end{figure}
